The Spine of American Legal Practice

### 2016-06-25 article/article.Rmd
Fix problem with display math

---
author:
- Kellen Funk
- Lincoln Mullen
documentclass: article
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    number_sections: False
title: The Spine of American Legal Practice
...

>>>>

---
author:
- Kellen Funk
- Lincoln Mullen
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    number_sections: False
    md_extensions: -tex_math_single_backslash
title: The Spine of American Legal Practice
---
